\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
conclusions section

We extended the MoveIt! benchmarking architecture~\cite{cohen2012generic} with video recording capabilities to quickly generate a large number of trajectories. The MoveIt! architecture allows for the definition of environments, referred to as planning scenes, start and goal states for robots (motion planning queries). It also allows for the use of any supported planning algorithms (planners). A combination of different scenes, motion queries, and planners was used to generate robot trajectories for evalutation. We chose three distinct scenes (Fig.~\ref{fig:scenes}): a kitchen (Countertop), an industrial workbench (Industrial) and a drawer on a table (Drawer). Multiple queries were generated in each scene for trajectories of the right arm of the PR2 robot (Fig.~\ref{fig:PR2}. The robot was positioned in the scenes manually and motion planning queries were constructed by hand. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

@@

The planning algorithms that we used are RRT-Connect~\cite{kuffner2000rrt} and RRT*.  RRT*~\cite{frazzoli-RRTstar} was used with two different cost functions: PathLength and MaxMinClearance.The objective for PathLength minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for MaxMinClearance computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize. Both planners are implemented in the OMPL library~\cite{OMPL:2012}. The planned trajectories are post-processed by an iterative-time parameterization method that time-parameterizes the trajectories while taking into account velocity and accelerations. The infrastructure we designed around MoveIt! allows us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. A total of 103 different trajectories were generated in this manner.

@@

>>>>

We extended the MoveIt! benchmarking architecture~\cite{cohen2012generic} with video generation capabilities to automate the generation of a large number of trajectories. The MoveIt! architecture allows for the definition of environments, referred to as planning scenes, start and goal states for robots (motion planning queries). It also allows for the use of any supported planning algorithms (planners). A combination of different scenes, motion queries, and planners was used to generate robot trajectories for evalutation. We chose three distinct scenes (Fig.~\ref{fig:scenes}): a kitchen (Countertop), an industrial workbench (Industrial) and a drawer on a table (Drawer). Multiple queries were generated in each scene for trajectories of the right arm of the PR2 robot (Fig.~\ref{fig:PR2}. The robot was positioned in the scenes manually and motion planning queries were constructed by hand. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

@@

The planning algorithms that we used are RRT-Connect~\cite{kuffner2000rrt} and RRT*.  RRT*~\cite{frazzoli-RRTstar} was used with two different cost functions: PathLength and MaxMinClearance.The objective for PathLength minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for MaxMinClearance computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize. Both planners are implemented in the OMPL library~\cite{OMPL:2012}. All the paths generated by RRT-Connect are shortcutted for a finite amount of time to improve the quality of the paths. The planned trajectories are post-processed by an iterative-time parameterization method that time-parameterizes the trajectories while taking into account velocity and accelerations. The infrastructure we designed around MoveIt! allows us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. A total of 103 different trajectories were generated in this manner.

Our main focus in generating trajectories was to generate a wide sample. The choice of planners used to generate the trajectory was not important. We preferred the randomized planners since they natively generate a wide variety of plans that are less likely to be similar to each other. We could have chosen to generate all our trajectories with an  asymptotically optimal planner like RRT* but we would not have been able to generate a variety of plans. This would also have restricted the richness of the trajectory features we could work with. Our intent in this work is not to evaluate particular planning algorithms but instead to examine the preference that human-observers have for generated trajectories regardless of the methods used to generate them.

@@

The classification results clearly show the value in using a data-driven approach to determining human preferences for robot trajectories. It is difficult, 
in obstacle filled cluttered environments, to hand-design an appropriate cost function for generating human preferred trajectories. Tuning coefficients 
and weights for all the individual cost components for designing preferred trajectories requires significant effort. 
The classifiers that we have built give us a notion of the quality of trajectories 
being generated without an explicit need to model the cost function. The output from the classifier could be integrated into gradient-free motion planning schemes 
(e.g. STOMP or a simulated annealing approach) as a cost for a particular trajectory. The identification of the key features that are important in defining a preferred trajectory 
should also help in the design of cost functions, when necessary, especially since some the features may not be traditionally included as part of a cost function. 
In particular, note that a feature like wrist\_tool\_dtw is not used in typical optimization schemes like RRT* which mostly relies on a path length optimization criterion.

\section{Conclusion}
In this work, we have generated ratings for a large dataset of robot trajectories. We have already gained significant insights into the 
types of trajectories that are preferred by human observers. In particular, we have been able to identify a set of features that seem to influence 
the human's perception of the trajectories the most. This can help us in defining better cost functions when generating the trajectories. The classifiers 
that we have learned could also be used to directly inform gradient free motion planning algorithms by assigning a rating to new trajectories. Our 
results were generated using a single robot model (the PR2) but we believe that they will easily translation to other robot models as well. To this end, 
we will keep the survey open and attempt to collect data for a larger set of trajectories in 
more environments and with different robots.

The dataset we have collected and the analysis we have already done in this paper will serve as a
 platform for further development of the idea of using 
a data-driven approach to motion planning. We intend to attempt to learn a cost function for describing the relation between the features and 
the ratings of the generated trajectories using inverse reinforcement learning. We hope to examine whether a cost function derived in this manner will 
lead to generation of more preferred trajectories. We would also like to extend our set of features to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.
